\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-01-18 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
switched to Fortran2003 in the manual

All SPECFEM3D Cartesian software is written in Fortran90 with full portability
in mind, and conforms strictly to the Fortran95 standard. It uses
no obsolete or obsolescent features of Fortran77. The package uses
parallel programming based upon the Message Passing Interface (MPI)
\citep{GrLuSk94,Pac97}.\\

@@

Then, to configure the software for your system, run the
\texttt{configure} shell script. This script will attempt to guess
the appropriate configuration values for your system. However, at
a minimum, it is recommended that you explicitly specify the appropriate
command names for your Fortran90 compiler and MPI package:

@@

\begin{description}
\item [{\texttt{F90}}] Path to the Fortran90 compiler.
\item [{\texttt{MPIF90}}] Path to MPI Fortran90.
\item [{\texttt{MPI\_FLAGS}}] Some systems require this flag to link to
MPI libraries.
\item [{\texttt{FLAGS\_CHECK}}] Compiler flags.
\end{description}
The configuration script automatically creates for each executable a corresponding
\texttt{Makefile} in the \texttt{src/} subdirectoy.
The \texttt{Makefile} contains a number of suggested entries for various
compilers, e.g., Portland, Intel, Absoft, NAG, and Lahey. The software
has run on a wide variety of compute platforms, e.g., various PC clusters
and machines from Sun, SGI, IBM, Compaq, and NEC. Select the compiler
you wish to use on your system and choose the related optimization
flags. Note that the default flags in the \texttt{Makefile} are undoubtedly
not optimal for your system, so we encourage you to experiment with
these flags and to solicit advice from your systems administrator.
Selecting the right compiler and optimization flags can make a tremendous
difference in terms of performance. We welcome feedback on your experience
with various compilers and flags.

@@

   Examine the log file 'config.log'. It contains detailed informations.
   In many cases, the path's to these specific compiler commands F90,
   CC and MPIF90 won't be correct if `./configure` fails.

@@

  Normally, this message will appear when you're mixing two different Fortran
  compilers. That is, using e.g. gfortran to compile non-MPI files
  and mpif90, wrapper provided for e.g. ifort, to compile MPI-files.

>>>>

All SPECFEM2D software is written in Fortran2003 with full portability
in mind, and conforms strictly to the Fortran2003 standard. It uses
no obsolete or obsolescent features of Fortran. The package uses
parallel programming based upon the Message Passing Interface (MPI)
\citep{GrLuSk94,Pac97}.\\

@@

Then, to configure the software for your system, run the
\texttt{configure} shell script. This script will attempt to guess
the appropriate configuration values for your system. However, at
a minimum, it is recommended that you explicitly specify the appropriate
command names for your Fortran compiler and MPI package:

@@

\begin{description}
\item [{\texttt{F90}}] Path to the Fortran compiler.
\item [{\texttt{MPIF90}}] Path to MPI Fortran.
\item [{\texttt{MPI\_FLAGS}}] Some systems require this flag to link to
MPI libraries.
\item [{\texttt{FLAGS\_CHECK}}] Compiler flags.
\end{description}
The configuration script automatically creates for each executable a corresponding
\texttt{Makefile} in the \texttt{src/} subdirectoy.
The \texttt{Makefile} contains a number of suggested entries for various
compilers, e.g., Portland, Intel, Absoft, NAG, and Lahey. The software
has run on a wide variety of compute platforms, e.g., various PC clusters
and machines from Sun, SGI, IBM, Compaq, and NEC. Select the compiler
you wish to use on your system and choose the related optimization
flags. Note that the default flags in the \texttt{Makefile} are undoubtedly
not optimal for your system, so we encourage you to experiment with
these flags and to solicit advice from your systems administrator.
Selecting the right compiler and optimization flags can make a tremendous
difference in terms of performance. We welcome feedback on your experience
with various compilers and flags.

@@

   Examine the log file 'config.log'. It contains detailed informations.
   In many cases, the paths to these specific compiler commands F90,
   CC and MPIF90 will not be correct if `./configure` fails.

@@

  Normally, this message will appear when you are mixing two different Fortran
  compilers. That is, using e.g. gfortran to compile non-MPI files
  and mpif90, wrapper provided for e.g. ifort, to compile MPI-files.
